Ecuador plant species BIEN Cleaning

### 2022-11-30 code/L1/L1_Ecuador_plants_BIEN.Rmd
change variable name

# Pre-filter
```{r}
# Flag records missing species names
check_pf <-
  bdc_scientificName_empty(
  data = Ecuador_BIEN_occ,
  sci_name = "scrubbed_species_binomial")
```

>>>>

# Pre-filter
```{r}
# Flag records missing species names
check_pf <-
  bdc_scientificName_empty(
  data = Ecuador_BIEN_occurrence,
  sci_name = "scrubbed_species_binomial")
```
